PAMELA: an annotation-based Java Modeling Framework

### 2021-02-09 architecture.tex
typos

A \texttt{PAMELAModel} is defined as a set of references to \texttt{ModelEntity}. A \texttt{ModelEntity} reflects a concept and is encoded in a Java \texttt{interface}. PAMELA metamodel allows multiple inheritance: thus \texttt{ModelEntity} may define a set of parent entities. Note that reification of \texttt{ModelEntity} is performed in a Java \texttt{interface} (and not a class), which only defines API whithout any implementation for methods. 
Note that \emph{ModelEntities} may declare \emph{ImplementationClasses}, which will be responsible for providing custom code implementing domain or application specific behaviour. A partially implemented \texttt{abstract} Java \texttt{class} may be defined as partial base implementation (conforms to implemented interface).

@@

PAMELA model at runtime is computed dynamically, working on the classpath of
launched Java application, and starting from a simple Java interface (or a
collection of Java interfaces) which is/are PAMELA-annotated. From a
mathematical point of view, internal representation of the underlying model is
a graph whose vertices are PAMELA \emph{ModelEntities} (annotated Java
interface), and edges are either inheritance links or reference links (a
property whose type is another \emph{ModelEntity}). \mytexttt{@Imports} and
  \mytexttt{@Import} annotations allows to include some other
  \emph{ModelEntities} in the model. On the contrary, an annotation attribute
  \mytexttt{@Getter(...ignoreType=true)} allows to ignore the link. In that
  context, PAMELA model computation is a graph closure computation, starting
  from a collection of vertices.

@@

PAMELA instances (instances of \emph{ModelEntity}) are handled though the use of \mytexttt{ModelFactory}, which is instantiated from a \mytexttt{ModelContext}.

>>>>

A \texttt{PAMELAModel} is defined as a set of references to \texttt{ModelEntity}. A \texttt{ModelEntity} reflects a concept and is encoded in a Java \texttt{interface}. PAMELA metamodel allows multiple inheritance: thus \texttt{ModelEntity} may define a set of parent entities. Note that reification of \texttt{ModelEntity} is performed in a Java \texttt{interface} (and not a class), which only defines API whithout any implementation for methods. 
Note that \emph{ModelEntities} may declare \emph{ImplementationClasses}, which
will be responsible for providing custom code implementing domain or
application specific behaviour. A partially implemented \texttt{abstract} Java
\texttt{class} may be defined as partial base implementation (conforms to
implemented interface), \jcb{as default methods in Java interfaces would be
(since Java 8).}

@@

PAMELA model at runtime is computed dynamically, working on the classpath of
launched Java application, and starting from a simple Java interface (or a
collection of Java interfaces) which is/are PAMELA-annotated. From a
mathematical point of view, internal representation of the underlying model is
a graph whose vertices are PAMELA \emph{ModelEntities} (annotated Java
interface), and edges are either inheritance links or reference links (a
property whose type is another \emph{ModelEntity}). \mytexttt{@Imports} and
  \mytexttt{@Import} annotations allow to include some other
  \emph{ModelEntities} in the model. An annotation attribute
  \mytexttt{@Getter(...ignoreType=true)} allows to ignore the link. In that
  context, PAMELA model computation is a graph closure computation, starting
  from a collection of vertices.

@@

PAMELA instances (instances of \emph{ModelEntity}) are handled through the use of \mytexttt{ModelFactory}, which is instantiated from a \mytexttt{ModelContext}.
